### 2023-01-05 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@ab62cf600d034460d39948077a44200a6a67d657 🚀

Here, we illustrate how our confidence that a pair of species never
interacts highly depends on sampling effort. We suggest that surveys of
species interactions can benefit from simulation modeling of the
sampling process. We demonstrate that the realized false-negative rate
of interactions is directly related to the relative abundance of the
species pool, and demonstrate how simulation can be used to produce a
null estimate of the false-negative rate given total sampling effort
(the total count of all individuals of all species seen). We also
introduce a method for resampling of model predictions of interaction
probability to account for observation error. We show that positive
associations in co-occurrence data can increase the realized number of
false-negatives, and demonstrate these positive associations are rampant
in network datasets. We conclude by recommending that the simulation of
sampling effort and species occurrence can and should be used to help
design surveys of species interaction diversity (Moore \& McCarthy
2016), and by advocating use of null models like those presented here as
a tool for both guiding design of surveys of species interactions and
for modeling detection error in predictive models.

@@

We start with a naive model of interaction detection: we assume that
every interacting pair of species is incorrectly observed as
not-interacting with an independent and fixed probability, which we
denote \(p_fn\) and subsequently refer to as the False-Negative Rate
(FNR). If we observe the same species not-interacting \(N\) times, then
the probability of a true-negative (denoted \(p_{tn}\)) is given by
\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
geometric distribution, a special case of the negative-binomial
distribution) is shown in fig.~\ref{fig:geometric}(A) for varying values
of \(p_{fn}\) and illustrates a fundamental link between our ability to
reliably say an interaction doesn't exist---\(p_{tn}\)---and the number
of times \(N\) we have observed a given species. In addition, note that
there is no non-zero \(p_{fn}\) for which we can ever \emph{prove} that
an interaction does not exist---no matter how many observations of
non-interactions \(N\) we have, \(p_{tn}<1\).

@@

\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}{%
\section{Resampling interaction probabilities to account for uncertainty
in detection
error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-detection-error}}

Here we show how to incorporate imperfect detection (both
false-negatives and false-positives) into model predictions of
interaction probability. Models for interaction prediction typically
yield a probability of interaction between each pair of species. When
these are considered with uncertainty, it is usually model-uncertainty,
e.g.~the variance in the interaction probability prediction across
several cross-validation folds, where the data is split into training
and test sets several times.Here we introduce a method for resampling
interaction probabilities (outlined in figure fig.~\ref{fig:resampling})
that simulates the observation process with prior estimates of both
false-negative and false-positive probabilities to produce an output
distribution of interaction probability that accounts for observation
error. We implement this in the software package
InteractionUncertaintySampler.jl.

@@

This method allows us to more effectively represent our uncertainty
about observation error in predictions of species interactions. This
also has implications for what we mean by `uncertainty' in interaction
predictions. A model's prediction can be `uncertain' in two different
ways: the model's predictions may have high variance, or the model's
predictions may be centered around a probability of interaction of
\(0.5\), where we are the most unsure about whether this interaction
exists. A more statistically robust framework for accounting for
different forms of uncertainty in probabilistic interaction predictions
seems a necessary goal that the field must undertake.

>>>>

Here, we illustrate how our confidence that a pair of species never
interacts highly depends on sampling effort. We suggest that surveys of
species interactions can benefit from simulation modeling of the
sampling process. We demonstrate how the realized false-negative rate of
interactions is related to the relative abundance of the species pool,
and use simulation to produce a null estimate of the false-negative rate
given total sampling effort (the total count of all individuals of all
species seen), and to introduce a method for resampling of model
predictions of interaction probability to account for observation error.
We then show that positive associations in co-occurrence data can
increase the realized number of false-negatives, and demonstrate these
positive associations are rampant in network datasets, and conclude by
recommending that the simulation of sampling effort and species
occurrence can and should be used to help design surveys of species
interaction diversity (Moore \& McCarthy 2016), and by advocating use of
null models like those presented here as a tool for both guiding design
of surveys of species interactions and for modeling detection error in
predictive models.

@@

We start with a naive model of interaction detection: we assume that
every interacting pair of species is incorrectly observed as
not-interacting with an independent and fixed probability, which we
denote \(p_{fn}\) and subsequently refer to as the False-Negative Rate
(FNR). If we observe the same species not-interacting \(N\) times, then
the probability of a true-negative (denoted \(p_{tn}\)) is given by
\(p_{tn}=1-(p_{fn})^N\). This relation (the probability-mass-function of
geometric distribution, a special case of the negative-binomial
distribution) is shown in fig.~\ref{fig:geometric}(A) for varying values
of \(p_{fn}\) and illustrates a fundamental link between our ability to
reliably say an interaction doesn't exist---\(p_{tn}\)---and the number
of times \(N\) we have observed a given species. In addition, note that
there is no non-zero \(p_{fn}\) for which we can ever \emph{prove} that
an interaction does not exist---no matter how many observations of
non-interactions \(N\) we have, \(p_{tn}<1\).

@@

\hypertarget{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}{%
\section{Resampling interaction probabilities to account for uncertainty
in observation
error}\label{resampling-interaction-probabilities-to-account-for-uncertainty-in-observation-error}}

Here we show how to incorporate imperfect observation (both
false-negatives and false-positives) into model predictions of
interaction probability. Models for interaction prediction typically
yield a probability of interaction between each pair of species. When
these are considered with uncertainty, it is usually model-uncertainty,
e.g.~the variance in the interaction probability prediction across
several cross-validation folds, where the data is split into training
and test sets several times. Here we introduce a method for resampling
interaction probabilities (outlined in figure
fig.~\ref{fig:resampling_concept}) that simulates the observation
process with prior estimates of both false-negative and false-positive
probabilities to produce an output distribution of interaction
probabilities that accounts for observation error. We implement this in
the software package InteractionUncertaintySampler.jl.

@@

This method allows us to more effectively represent our uncertainty
about observation error in predictions of species interactions. This
also has implications for what we mean by `uncertainty' in interaction
predictions. A model's prediction can be `uncertain' in two different
ways: the model's predictions may have high variance, or the model's
predictions may be centered around a probability of interaction of
\(0.5\), where we are the most unsure about whether this interaction
exists. Improving the incorporation of different forms of uncertainty in
probabilistic interaction predictions seems a necessary next step toward
understanding what pairs of species we know the least about, in order to
prioritize sampling to provide the most new information possible.
